FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-01-13 ECOOP18/sections/RelatedWork.tex
Polished text

\noindent  {\bf Languages using hygienicity.}
In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316}, HygJava~\cite{kusmierek2007hygienic} and Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is proposed to deal with unintentional method conflicts, which is basically giving a method a unique identifier by prefixing the name with an unambiguous path. The advantage of this approach, compared to ours, is that it does not require additional notion in the method dispatching. However, the disadvantage is that these approaches depend on name appending. As shown in Figure~\ref{fig:magda_code}, two methods \lstinline|m| from different branches \lstinline|A| and \lstinline|B| cannot be overridden by the method \lstinline|m| in \lstinline|C| because they are regarded as unrelated methods, since in these hygienic approaches, path names are used to distinguish different methods.  Moreover, writing programs in these languages is tedious if not supported by an ad-hoc IDE and the path prefix is mandatory even if it is not needed in some scenarios. Finally, the multiple inheritance model in Magda is based on Mixins, whereas \MIM{} is based on traits. Thus, Magda inherits all limitations of Mixins (such as the linearization problem, etc).

>>>>

\noindent  {\bf Languages using hygienicity.}
In NextGen/MixGen~\cite{Allen:2003:FAG:949305.949316},
HygJava~\cite{kusmierek2007hygienic} and
Magda~\cite{Bono:2012:MNL:2367163.2367198}, \emph{hygienicity} is
proposed to deal with unintentional method conflicts. The idea is 
to give a method a unique identifier by prefixing the name
with an unambiguous path. As shown in Figure~\ref{fig:magda_prefix},
the prefix \lstinline|HelloWorld| in method call \lstinline|(new HelloWorld []).HelloWorld.MainMatter()| is mandatory. So writing programs in these languages is
tedious if not supported by a specialized IDE, that aids filling
prefix/method information.  The advantage of this
approach, compared to ours, is that it does not require any additional
notion for method dispatching. Indeed
the compilation strategy is simple, just by generating conventional code (say
in Java or C++) with
method names attached with prefixes. Unfortunatelly the disadvantage
is that some expressive power is lost. In particular \emph{merging}
methods arizing from diamond inheritance is not possible because the 
methods have different prefixes. 
As shown in Figure~\ref{fig:magda_code}, two methods
\lstinline|m| from different branches \lstinline|A| and \lstinline|B|
cannot be overridden by the method \lstinline|m| in \lstinline|C|
because they are regarded as unrelated methods, and \lstinline|m| in
\lstinline|C| is just another new method that has nothing to do with
\lstinline|A.m| or \lstinline|B.m|. The reason is that in these
hygienic approaches, path names are used to distinguish different
methods. In contrast, our model can deal with unintentional conflicts,
as well as merged methods because our semantics is not simply based on
prefixing. Instead, our model keeps the names of methods unchanged,
and our direct operational semantics takes static and
dynamic type information into account at runtime when doing method
dispatching. Finally, the multiple inheritance model in Magda is based on
Mixins, whereas \MIM{} is based on traits. Thus, Magda inherits all
limitations of Mixins (such as the linearization problem, etc).

\begin{figure}[t]
	\saveSpaceFig
	\begin{lstlisting}
mixin HelloWorld of Object =
	new Object MainMatter()
	begin
		"Hello world".String.print();
	end;
end;
(new HelloWorld []).HelloWorld.MainMatter();
	\end{lstlisting}
	\caption{Full-qualified name of method call in Magda.}
	\label{fig:magda_prefix}
	\saveSpaceFig
\end{figure}
